---
title: "p8105_hw5_wx2233"
author: "Weijia Xiong"
date: "10/31/2019"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
set.seed(1)
```


## Problem 1
```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))


```



There are two cases to address:

For numeric variables, you should fill in missing values with the mean of non-missing values
For character variables, you should fill in missing values with "virginica"

Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.


```{r}
## fill function
my_fill = function(x) {
  if (is.numeric(x)) {
     x = replace_na(x,round(mean(x,na.rm = TRUE),1))
  }
  else if (is.character(x)) {
     x = replace_na(x,"virginica")
  }
  x
}

## apply using map
map(iris_with_missing, my_fill) %>% 
bind_cols()
```


## Problem 2

This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

### Create a tidy dataframe
```{r message=FALSE, warning=FALSE}
file_list = list.files("./data")

read_data = function(x) {
  path = str_c("./data/",x)
  read_csv(path) %>% 
    janitor::clean_names()
}

new_data = 
  purrr::map(file_list,read_data) %>% 
  bind_rows() %>% 
  mutate(file_names = file_list) %>% 
  separate(file_names, into = c("group", "id"), sep = "_") %>% 
  mutate(
     id = str_remove(id,".csv")
  ) %>% 
  select(id,group,everything())

new_data %>% 
  knitr::kable()


```



### Plot

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
new_data %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week", 
    names_prefix = "week_",
    values_to = "observations"
    ) %>% 
ggplot(aes(x = week, y = observations)) +
  geom_line(aes(group = id,color = id)) +
  facet_grid(.~group) +
  labs(
    y = "Observations",
    x = "Week",
    title = "Observations on Each Subject Over Time"
  )
```

The experiment group's observations have a increasing trend with time while the control group's observations are flutuating. Also, the experiment group's observations are more than the observations of control group. 

## Problem 3


```{r}
set.seed(1)
sim_regression = function(beta1 = 0) {
  
  sim_data = tibble(
    x = rnorm(30, mean = 0, sd = 1),
    y = 2 + beta1 * x + rnorm(30, 0, sqrt(50))
  )
  
  ls_fit = 
    lm(y ~ x, data = sim_data) %>% 
    broom::tidy()
  
  tibble(
    beta1_hat = pull(ls_fit,estimate)[2],
    p_value = pull(ls_fit,p.value)[2]
  )
  
}

```


## 
```{r}
sim_results = 
  rerun(10000, sim_regression(0)) %>%  ## rerun
  bind_rows()
```


```{r}

# sim_results_all = 
#   tibble(beta_1 = c(1, 2, 3, 4, 5, 6)) %>% 
#   mutate(
#     output_list = map(.x = beta_1, sim_regression)) %>% 
#   unnest


sim_results_all = 
  tibble(beta_1 = c(1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_list = map(.x = beta_1, ~rerun(10000,sim_regression(beta1 = .x)))
    ) %>% 
  unnest %>% 
  unnest
```


### Power
Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of β2 on the x axis. Describe the association between effect size and power.

```{r}
power_data = 
sim_results_all %>% 
  filter(p_value < 0.05) %>% 
  group_by(beta_1) %>% 
  summarize(
    power = n()/10000
  )

power_data %>% 
  ggplot(aes(x = beta_1, y = power)) +
  geom_point(color = "red ", size = 5, alpha = 0.5) +
  geom_line()

```

Association: the power increases with the increasing of effect size.


### Plot of Estimate and True beta1


Make a plot showing the average estimate of β̂ 1 on the y axis and the true value of β1 on the x axis. Make a second plot (or overlay on the first) the average estimate of β̂ 1 only in samples for which the null was rejected on the y axis and the true value of β1 on the x axis. Is the sample average of β̂ 1 across tests for which the null is rejected approximately equal to the true value of β1? Why or why not?

```{r}
all_data = 
sim_results_all %>% 
  group_by(beta_1) %>% 
  summarize(
    avg_beta_hat_all = mean(beta1_hat)
  ) 
 
samples_data = 
sim_results_all %>% 
  filter(p_value < 0.05) %>% 
  group_by(beta_1) %>% 
  summarize(
    avg_beta_hat_sample = mean(beta1_hat)
  ) 

beta_data = left_join(all_data,samples_data)

beta_data %>% 
  ggplot(aes(x = beta_1, y = avg_beta_hat_all)) +
  geom_point(color = "red", size = 5, alpha = 0.5) +
  geom_line() +
  geom_point(aes(x = beta_1, y = avg_beta_hat_sample), color = "blue", size = 5, alpha = 0.5) +
  geom_line(aes(x = beta_1, y = avg_beta_hat_sample))

  
```


