---
title: "p8105_hw5_wx2233"
author: "Weijia Xiong"
date: "10/31/2019"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
set.seed(1)
```


## Problem 1
```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))


```



There are two cases to address:

For numeric variables, you should fill in missing values with the mean of non-missing values
For character variables, you should fill in missing values with "virginica"

Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.


```{r}
## fill function
my_fill = function(x) {
  if (is.numeric(x)) {
     x = replace_na(x,round(mean(x,na.rm = TRUE),1))
  }
  else if (is.character(x)) {
     x = replace_na(x,"virginica")
  }
  x
}

## apply using map
map(iris_with_missing, my_fill) %>% 
bind_cols()
```

